TBD

### 2016-10-14 paper.tex
polished off theCombining the result from Lu with the aformentioned two observations we made in regards to Eq.~\eqref{}
It now trivially follows \citet{Lu2015} from follows that we can apply the CG method to solve any normal equation. We have already

%It is a well known fact that the normal equation has at least one solution. If $\bB^H\bB$ is invertible then the solution that minimizes Eq.~\eqref{eq:norm_ls} is unique. In contrast, if $\bB^H\bB$ is singular there are an infinite amount of solutions
%that minimizes Eq.~\eqref{eq:norm_ls}.
%Interestingly enough, we can use the CG method to solv

\subsection{Computational Complexity}
\citet{Kaniel1966} was able to determine convergence bounds for CG using Chebyshev polynomials. A much more in depth analysis of CG convergence can be found in
\citep{Sluis1986}. As can be seen from Algorithm \ref{algo:CG}, the CG method makes use of a major outer loop (line 6 of Algorithm \ref{algo:CG}). It turns out that at worst 
the number of major iterations that CG requires to converge\footnote{If the $\bA$-norm is used to calculate the error.} is proportional to $\sqrt{\kappa}$, where $\kappa$ is the specctral condition number of the matrix $\bA$.
The mathematical definition of $\kappa(\bA)$ is
\begin{equation}
\label{eq:kappa}
\kappa(\bA) = \frac{\lambda_{\textrm{max}}}{\lambda_{\textrm{min}}}, 
\end{equation}
where $\lambda_{\textrm{max}}$ and $\lambda_{\textrm{min}}$ respectively denote the largest and the smallest eigenvalue of $\bA$.
Moreover, the most expensive operation that is conducted within each major loop of Algorithm~\ref{algo:CG} is the vector-matrix product $\bA\bp$, which has a complexity of $\mathbb{O}(m)$, where $m$ is the number of non-zero entries in $\bA$.
The computational complexity of CG is therefore 
\begin{equation}
\label{eq:cg_bound}
\mathbb{O}(\sqrt{\kappa}m). 
\end{equation}
It should now also be clear to the reader why the CG method is especially applicable to sparse linear systems, since in those cases $m < P^2$.

@@

\subsection{Normal Equation}
Lets assume that instead of Eq.~\eqref{eq:linear_system} we have a more general linear system, i.e.
\begin{equation}
 \bb = \bB\bx,
\end{equation}
where $\bb\in\mathbb{C}^K$, $\bx\in\mathbb{C}^P$  and $\bB\in\mathbb{C}^{K \times P}$, with $K > P$. We can use the normal equation 
\begin{equation}
\label{eq:normal_equation}
\bB^H\bB\bx = \bB^H\bb 
\end{equation}
to estimate the $\bx$ that minimizes
\begin{equation}
\label{eq:norm_ls}
\|\bb-\bB\bx\|_F^2. 
\end{equation}
There are a few important observations that we can make while inspecting Eq.~\eqref{eq:normal_equation}:
\begin{enumerate}
\item $\bB^H\bB$ is an Hermitian positive semi-definite square matrix by construction.
\item $\bB^H\bb$ is in the column range of $\bB^H\bB$; this follows trivially from 
\begin{equation}
\bB^H\bb \in \mathcal{R}(\bB^H) \implies \bB^H\bb \in \mathcal{R}(\bB^H\bB).   
\end{equation}
\end{enumerate}

Recall that we mentioned that in general we can only solve Eq.~\eqref{eq:linear_system} with CG if $\bA$ is an Hermitian positive-definite square matrix. Recently,
\citet{Lu2015} showed that the CG method has an even broader applicability, it can be used to solve Eq.~\eqref{eq:linear_system} even if $\bA$ is an Hermitian positive semi-definite
square Hermitian matrix as long as $\bb$ is in the column range of $\bA$. Combining the result from Lu with the aformentioned two observations we made in regards to Eq.~\eqref{}

It now trivially follows \citet{Lu2015} from follows that we can apply the CG method to solve any normal equation. We have already

%It is a well known fact that the normal equation has at least one solution. If $\bB^H\bB$ is invertible then the solution that minimizes Eq.~\eqref{eq:norm_ls} is unique. In contrast, if $\bB^H\bB$ is singular there are an infinite amount of solutions
%that minimizes Eq.~\eqref{eq:norm_ls}. 
%Interestingly enough, we can use the CG method to solve Eq.~\eqref{eq:normal_equation} in either one of the previously mentioned scenarios.

Moreover, we can use the CG method to solve Eq.~\eqref{eq:normal_equation}, since $\bA^H\bA$ is Hermitian by construction 
and $\bA^H\bb$ is in the column range of $\bA^H\bA$.
\begin{equation}
\bA^H\bb \in \mathcal{R}(\bA^H) \implies \bA^H\bb \in \mathcal{R}(\bA^H\bA).   
\end{equation}

>>>>

\subsection{Computational Complexity}
\citet{Kaniel1966} was able to determine convergence bounds for CG using Chebyshev polynomials. A much more in depth analysis of CG convergence can be found in
\citep{Sluis1986}. As can be seen from Algorithm \ref{algo:CG}, the CG method makes use of a major outer loop (line 6 of Algorithm \ref{algo:CG}). It turns out that at worst 
the number of major iterations that CG requires to converge\footnote{If the $\bA$-norm is used to calculate the error.} is proportional to $\sqrt{\kappa}$, where $\kappa$ is the spectral condition number of the matrix $\bA$.
The mathematical definition of $\kappa(\bA)$ is
\begin{equation}
\label{eq:kappa}
\kappa(\bA) = \frac{\lambda_{\textrm{max}}}{\lambda_{\textrm{min}}}, 
\end{equation}
where $\lambda_{\textrm{max}}$ and $\lambda_{\textrm{min}}$ respectively denote the largest and the smallest eigenvalue of $\bA$.
Moreover, the most expensive operation that is conducted within each major loop of Algorithm~\ref{algo:CG} is the vector-matrix product $\bA\bp$, which has a complexity of $\mathbb{O}(m)$, where $m$ is the number of non-zero entries in $\bA$.
The computational complexity of CG is therefore 
\begin{equation}
\label{eq:cg_bound}
\mathbb{O}(\sqrt{\kappa}m). 
\end{equation}
It should now also be clear to the reader why the CG method is especially applicable to sparse linear systems, since in those cases $m < P^2$.

@@

\subsection{Normal Equation}
Lets assume that instead of Eq.~\eqref{eq:linear_system} we have a more general linear system, i.e.
\begin{equation}
 \bb = \bB\bx,
\end{equation}
where $\bb\in\mathbb{C}^K$, $\bx\in\mathbb{C}^P$  and $\bB\in\mathbb{C}^{K \times P}$, with $K > P$. We can use the normal equation 
\begin{equation}
\label{eq:normal_equation}
\bB^H\bB\bx = \bB^H\bb 
\end{equation}
to estimate the $\bx$ that minimizes
\begin{equation}
\label{eq:norm_ls}
\|\bb-\bB\bx\|_F^2. 
\end{equation}
There are a few important observations that we can make while inspecting Eq.~\eqref{eq:normal_equation}:
\begin{enumerate}
\item $\bB^H\bB$ is a square positive semi-definite Hermitian matrix by construction.
\item $\bB^H\bb$ is in the column range of $\bB^H\bB$; this follows trivially from 
\begin{equation}
\bB^H\bb \in \mathcal{R}(\bB^H) \implies \bB^H\bb \in \mathcal{R}(\bB^H\bB).   
\end{equation}
\end{enumerate}

Recall that we mentioned that in general we can only solve Eq.~\eqref{eq:linear_system} with CG if $\bA$ is a square positive-definite Hermitian matrix. Recently,
\citet{Lu2015} showed that the CG method has an even broader applicability, it can be used to solve Eq.~\eqref{eq:linear_system} even if $\bA$ is an Hermitian positive semi-definite
square matrix as long as $\bb$ is in the column range of $\bA$.

In light of \citet{Lu2015}, the two observations in the numbered list we presented earlier in this section imply that Eq.~\eqref{eq:normal_equation}
can be solved by employing the CG method. The solution returned by CG is however only unique if $\bB^H\bB$ is positive-definite (invertible). The solution
obtained by CG, whether it be unique or not, does however minimize Eq.~\eqref{eq:norm_ls} in a least squares sense.

Note that if $\bA$ is positive semi-definite its smallest eigenvalue is zero, which implies that Eq.~\eqref{eq:kappa} is not defined. \citet{Lu2015} show that when $\bA$
is a square positive semi-definite Hermitian matrix we do not use the spectral condition number to bound the convergence complexity of CG, but the general spectral condition
number instead. The general spectral condition number is very similar to the spectral condition number, the only difference being that in Eq.~\eqref{eq:kappa} we replace  
$\lambda_{\textrm{min}}$ with $\lambda_{\textrm{min}}^+$, which denotes the smallest positive eigenvalue.
